### 2023-09-14 project_Luis_PhD/paper.tex
add abstract, correcions,  cites review

For the Run 2 and Run 3 luminosity measurements:
\begin{itemize}
\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
\item calculate the calibration constant (visible crossection) corresponding to 13 TeV proton-proton collision data,
\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers,
\item determine the instantaneous and the total integrated luminosity,
\item determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
\end{itemize}

\par
For the development of the HL-LHC upgrade system:
\begin{itemize}
\item study the different parts of the TEPX detector,
\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector,
\item develop algorithms for pixel  cluster counting and coincidence counting,
\item determine the linearity and  precision of the different methods.
\end{itemize}

@@

\item {\bf Semester 1 (2023-2)}:
  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments}
  \SubItem{ Review of the literature.}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}

\item {\bf Semester 2 (2024-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis}
  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
  \SubItem{ Start work on the 2023 dataset luminosity measurement. }

\item {\bf Semester 3 (2024-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Complete work on the 2023 dataset luminosity measurement. }
  \SubItem{ Start work on the 2024 dataset luminosity measurement. }

\item {\bf Semester 4 (2025-1)}:
  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC}
  \SubItem{ Writing of the monograph}

\item {\bf Semester 5 (2025-2)}:
  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}

\item {\bf Semester 6 (2026-1)}:
  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}

\item {\bf Semester 7 (2026-2)}:
  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
  \SubItem{ Writing of the Ph.D thesis}

\item {\bf Semester 8 (2027-1)}: 
  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
  \SubItem{ Defense of the Ph.D thesis}

>>>>

For the Run 2 and Run 3 luminosity measurements:
\begin{itemize}
\item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules.
\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
\item Calculate the calibration constant (visible crossection) corresponding to 13.6 TeV proton-proton collision data.
\item Study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers.
\item Determine the instantaneous and the total integrated luminosity.
\item Determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
\end{itemize}

\par
For the development of the HL-LHC upgrade system:
\begin{itemize}
\item Study the different parts of the TEPX detector.
\item Study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
\item Develop algorithms for pixel  cluster counting and coincidence counting.
\item determine the linearity and  precision of the different methods.
\end{itemize}

@@

\item {\bf Semester 1 (2023-2)}:
  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
  \SubItem{ Review of the literature.}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}

\item {\bf Semester 2 (2024-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
  \SubItem{ Start work on the 2023 dataset luminosity measurement. }

\item {\bf Semester 3 (2024-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
  \SubItem{ Start work on the 2024 dataset luminosity measurement. }

\item {\bf Semester 4 (2025-1)}:
  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
  \SubItem{ Writing of the monograph.}

\item {\bf Semester 5 (2025-2)}:
  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}

\item {\bf Semester 6 (2026-1)}:
  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}

\item {\bf Semester 7 (2026-2)}:
  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
  \SubItem{ Writing of the Ph.D thesis.}

\item {\bf Semester 8 (2027-1)}: 
  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
  \SubItem{ Defense of the Ph.D thesis.}
